---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# xmerit

<!-- badges: start -->
<!-- badges: end -->

The goal of `xmerit` is to facility teaching and  researching on Econometrics. 

## Installation

You can install the development version of xmerit from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("huhuaping/xmerit")
```

## Example

This is a basic example which shows you how to show math equation (`LaTex` equation) easily in Rmarkdown Writing.

### Dataset and model

```{r example, echo=TRUE}
library(xmerit)
data(mtcars)
## basic example code

df <- mtcars
mod <- mpg ~ cyl + disp + wt +gear

xvars <- all.vars(mod)[-1]
yvars <- all.vars(mod)[1]

lm.fit <- lm(formula = mod, data = df)
summary(lm.fit)

```

### xmerit::lx.psm


Here we will show the use of function `xmerit::lx.psm()`.


#### R chunk

```{r}
#| results = 'asis',
#| echo = TRUE,
#| eval = FALSE

lx.out <- xmerit::lx.psm(
  x = xvars, y = yvars,
  begin = 0,
  #greek.n = length(xvars)+1,
  n.row = 3,
  lm.label = "lx-psm",
  lm.tag = "lx.psm",
  no_dollar = FALSE)
```


#### source style

```
$$\begin{align}
\begin{split}
mpg_i=&+\beta_{0}+\beta_{1}cyl_i+\beta_{2}disp_i\\&+\beta_{3}wt_i+\beta_{4}gear_i+u_i
\end{split}
\quad \text{(lx.psm)}\quad
(\#eq:lx-psm)
\end{align}$$

The cross-reffer syntax of `see \@ref(eq:lx-psm)`  will be rendered as see \@ref(eq:lx-psm).
```
#### render effect

$$\begin{align}
\begin{split}
mpg_i=&+\beta_{0}+\beta_{1}cyl_i+\beta_{2}disp_i\\&+\beta_{3}wt_i+\beta_{4}gear_i+u_i
\end{split}
\quad \text{(lx.psm)}\quad
(\#eq:lx-psm)
\end{align}$$

The cross-reference syntax of `see \@ref(eq:lx-psm)`  will be rendered as see \@ref(eq:lx-psm).

### xmerit::lx.est

Now let me show the use of function `xmerit::lx.est()`.

#### R chunk

```{r}
#| results = 'asis',
#| echo = TRUE,
#| eval = FALSE

lx.out <- xmerit::lx.est(
  lm.mod = mod, lm.dt = df,
  lm.n = 3, lm.label = "lx-est", 
  lm.tag = "lx.est",
  no_dollar = FALSE)
```


#### source style

```
$$\begin{equation}
\begin{alignedat}{999}
&\widehat{mpg}=&&+43.54&&-1.78cyl_i&&+0.01disp_i\\ 
&(s)&&(4.8601)&&(0.6139)&&(0.0120)\\ 
&(t)&&(+8.96)&&(-2.91)&&(+0.58)\\ 
&(cont.)&&-3.79wt_i&&-0.49gear_i &&\\ 
&(s)&&(1.0818)&&(0.7903) &&\\ 
&(t)&&(-3.51)&&(-0.62) &&
\end{alignedat}
\quad \text{(lx.est)}\quad
(\#eq:lx-est)
\end{equation}$$

The cross-reference syntax of `see \@ref(eq:lx-est)`  will be rendered as see \@ref(eq:lx-est).
```
#### render effect

$$\begin{equation}
\begin{alignedat}{999}
&\widehat{mpg}=&&+43.54&&-1.78cyl_i&&+0.01disp_i\\ 
&(s)&&(4.8601)&&(0.6139)&&(0.0120)\\ 
&(t)&&(+8.96)&&(-2.91)&&(+0.58)\\ 
&(cont.)&&-3.79wt_i&&-0.49gear_i &&\\ 
&(s)&&(1.0818)&&(0.7903) &&\\ 
&(t)&&(-3.51)&&(-0.62) &&
\end{alignedat}
\quad \text{(lx.est)}\quad
(\#eq:lx-est)
\end{equation}$$

The cross-reference syntax of `see \@ref(eq:lx-est)`  will be rendered as see \@ref(eq:lx-est).
